Impacts of Social Backgrounds on People's Perception of the Risk of Getting AIDS

### 2022-04-11 outputs/paper/paper.Rmd
Update paper.Rmd

age_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Female)",
    x = "age",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r numm, fig.cap="Percentage Distribution of Survey Answers by Age", echo = FALSE,fig.width=8, fig.height=4}

@@

num_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Male)",
    x = "No. of sexual partner other than Wife",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r numvf, fig.cap="Percentage Distribution of Survey Answers by Number of Sexual Partners", echo = FALSE,fig.width=8, fig.height=4}

@@

num_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Female)",
    x = "No. of sexual partner other than Husband",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```

@@

education_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Male)",
    x = "Education",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r eduf, fig.cap="Percentage Distribution of Survey Answers by Education Level", echo = FALSE, fig.width=8, fig.height=4}

education_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Female)",
    x = "Education",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r maritalm, fig.cap="Percentage Distribution of Survey Answers by Marital Status",  echo = FALSE, fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Male)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r maritalf, fig.cap="Percentage Distribution of Survey Answers by Marital Status", echo = FALSE, fig.width=8, fig.height=4}

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r resm, fig.cap="Percentage Distribution of Survey Answers by Residence",  echo = FALSE, fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Male)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r resf, fig.cap="Percentage Distribution of Survey Answers by Residence", echo = FALSE, fig.width=8, fig.height=4}

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What is your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
\newpage
# References

>>>>

age_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "age",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r numm, fig.cap="Percentage Distribution of Survey Answers by Age", echo = FALSE,fig.width=8, fig.height=4}

@@

num_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Male)",
    x = "No. of sexual partner other than Wife",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r numvf, fig.cap="Percentage Distribution of Survey Answers by Number of Sexual Partners", echo = FALSE,fig.width=8, fig.height=4}

@@

num_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "No. of sexual partner other than Husband",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```

@@

education_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Male)",
    x = "Education",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r eduf, fig.cap="Percentage Distribution of Survey Answers by Education Level", echo = FALSE, fig.width=8, fig.height=4}

education_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "Education",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r maritalm, fig.cap="Percentage Distribution of Survey Answers by Marital Status",  echo = FALSE, fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Male)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r maritalf, fig.cap="Percentage Distribution of Survey Answers by Marital Status", echo = FALSE, fig.width=8, fig.height=4}

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r resm, fig.cap="Percentage Distribution of Survey Answers by Residence",  echo = FALSE, fig.width=8, fig.height=4}

@@

marital_diverging %>% filter(gender == "male")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c  ("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "darkslategray4",
      "small" = "darkslategray2",
      "moderate" = "deepskyblue2",
      "great" = "deepskyblue4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Male)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
```{r resf, fig.cap="Percentage Distribution of Survey Answers by Residence", echo = FALSE, fig.width=8, fig.height=4}

marital_diverging %>% filter(gender == "female")%>%
  ggplot(aes(
    x = demographic_info,
    y = chances_of_getting_aids,
    fill = survey_answer
  )) + geom_col() +
  geom_text(aes(label = percent_label),
    position = position_stack(vjust = 0.5),
    color = "white",
    fontface = "bold"
  ) +
  coord_flip() +
  scale_x_discrete() +
  scale_fill_manual(
    breaks = c("no risk at all", "small", "moderate", "great"),
    values = c(
      "no risk at all" = "pink4",
      "small" = "pink2",
      "moderate" = "brown2",
      "great" = "brown4"
    )
  ) +
  labs(
    title = "What are your chances of getting AIDS? (Female)",
    x = "Marital Status",
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    axis.title.y = element_text(margin = margin(r = 20)),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    panel.grid = element_blank(),
    legend.position = "top"
  )
```
\newpage
# References
